Reasoning About a Machine with Local Capabilities

### 2019-08-19 toplas/paper.tex
[TOPLAS] Rewrite extensional discussion

\begin{toplas}
  In order to be able to solve the recursive domain equation, we want the future world relations to be extensional.
  Intuitively, the future world relation specifies how memory protocols may change over time.
  If the future world relation was not extensional, then the protocols could just disappear entirely regardless of what they promise.
  A piece of memory can still be repurposed under the right circumstances, i.e., if the protocol allows it under the future world relation used.
  In practice, the extensionality of future worlds means that a future world cannot forget about region names in a past world.
  This is the reason we use masks rather than deleting the regions altogether.
  It does not, however, matter what kind of region is used as a mask; it is the region name we must retain.
  This is why we allow revoked regions to be replaced by other regions in the two future world relations.
  This may seem unnecessary as the future world relation allows new regions to be added.
  However, for technical reasons in private future worlds, we need to be able to reinstate old regions with the same region names as they had in a past world.
  Further, we do not want public future worlds to be able to prevent reinstation in private future worlds.
  Private future worlds cannot revoke permanent regions, so we cannot allow public future worlds to use permanent regions as masks for revoked regions.
\end{toplas}

>>>>

\begin{toplas}
  Intuitively, the future world relation specifies how memory protocols may change over time.
  Rather than deleting regions in future worlds, we follow the approach in \citet{Thamsborg:2011:KLR:2034773.2034831,Ahmed2004semantics} and use masks to signal which regions are active.
  This approach implies that the future world relation is a preorder and hence we can use the
  method in \citet{Birkedal:2011:SKM:1926385.1926401,Birkedal:tutorial-notes} to solve the recursive world equation.
\end{toplas}
